
---
output:
  md_document:
    variant: markdown_github
---

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jaytimm/quicknews.svg?branch=main)](https://travis-ci.com/jaytimm/quicknews)
<!-- badges: end -->


# quicknews 

Some R-based tools for working with digital media, including functions for:

(1) extracting metadata for articles posted on Google News;
(2) resolving shortened URLs; and
(3) scraping online news article content per user-specified URL.



## Installation

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
```


```{r eval=FALSE}
devtools::install_github("jaytimm/quicknews")
```



## Usage

### ยง Google News metadata

The `qnews_get_newsmeta` retrieves metadata from news articles posted to Google News.  There are two search parameters: `term` & `since`.  By default, metadata for articles included in the Headlines section are extracted.  Options for the `since` parameter include `1y`, `1d`, and `7d`.

```{r}
metas <- quicknews::qnews_get_newsmeta (term = NULL, since = NULL)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
metas %>%
  arrange(desc(date)) %>%
  select(-link) %>%
  slice(1:5) %>%
  knitr::kable()
```




### ยง Article content

The `qnews_extract_article` functions scrapes web content from URLs specified in the `links` parameter.  Via `rvest` and `xml2`.  The function contains a simple filter for culling html nodes not relevant to article content.  It is not perfect -- no article extractor is -- but no Java dependencies. 

```{r}
articles <- quicknews::qnews_extract_article(metas$link[1:5])

list(title = strwrap(articles$title[1], width = 60), 
     text = strwrap(articles$text[1], width = 60)[1:10])
```

```{r eval=FALSE}
articles2 <- parallel::mclapply(metas$link,
                                quicknews::qnews_extract_article,
                                mc.cores = 6)
```



### ยง Resolve shortened urls

Shortened URLs are generally encountered in social media.  So, we build a simple demonstration Twitter corpus.

```{r message=FALSE, warning=FALSE}
some_tweets <- rtweet::search_tweets2(q = '#elections2022', 
                                      include_rts = F,
                                      n = 1000)
```


The `qnews_clean_urls` function extracts source info from URL links and identifies whether or not link has been shortened.  The latter is accomplish using a simple dictionary of common shortening services (eg, *bitly.com* & *tinyurl.com*)

```{r}
clean_urls <- quicknews::qnews_clean_urls(url = some_tweets$urls_url)

head(clean_urls)
```


The `qnews_unshorten_urls` can then be used to resolve shortenened URLs.

```{r}
shorts <- subset(clean_urls, is_short == 1)
longs <- quicknews::qnews_unshorten_urls(x = shorts$urls_url)

head(longs)
```


